### 2022-12-29 tesis_Rodolfo/Abstract/abstract.tex
Rodolfo Thesis

\begin{abstract}
\begin{center}
    {\huge Abstract}
\end{center}
    van der Meer calibration is decribed
\end{abstract}

>>>>

\begin{abstract}
\begin{center}
    {\huge Abstract}
\end{center}
The calibration of the luminosity measurement from the analysis of the van der Meer scan program by the CMS experiment in the 2018 proton-proton data taking at $\sqrt{s}=$13 TeV with the CMS Silicon Pixel detector is reported. The recorded data was reprocessed using a selection of the Pixel detector corresponding to the period from 2018-05-28 to 2018-07-07, based on luminosity stability studies. The background estimation corresponding to this module selection is reported. The analysis of the van der Meer scans presented here results in the calibration constant $\sigma_{vis}= 9229 \pm 8 (\text{stat.}) \pm 28 (\text{syst.})\text{ mb}$.

\end{abstract}

### 2022-12-29 tesis_Rodolfo/Abstract/resumen.tex
Rodolfo Thesis

\begin{abstract}
    \begin{center}
    {\huge Resumen}
\end{center}
Calibracion de van der Meer
\end{abstract}

>>>>

\begin{abstract}
    \begin{center}
    {\huge Resumen}
\end{center}
Se reporta la calibraci\'on de la medici\'on de luminosidad realizada a trav\'es del programa de escaneo de van der Meer del CMS en 2018 en la toma de datos prot\'on-prot\'on a $\sqrt{s}=$13 TeV, para el detector de pixeles de silicio (Silicon Pixel detector). Los datos han sido reprocesados aplicando una selecci\'on de m\'odulos del detector de pixeles que corresponde al periodo 28/05/2018 a 07/07/2018, basada en un estudio de estabilidad de luminosidad. La estimaci\'on del ruido de fondo en las mediciones correspondiente a esta selecci\'on de m\'odulos es tambi\'en reportada.  El an\'alisis de los escaneos de van der Meer presentados en este trabajo resulta en la constante de calibraci\'on $\sigma_{vis}= 9229 \pm 8 (\text{stat.}) \pm 28 (\text{syst.})\text{ mb}$. 
\end{abstract}
